---
title: "USA Poll Analysis"
format: html
execute: 
  echo: false

---


```{r}
#| message: false
#| warning: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
model <- lm(mpg ~ wt + hp, data = mtcars)
# summary(model)

```
$$P(Y = 1) = \frac{1}{1 + e^{-(\beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n)}}$$

with $Y \sim \text{Bernoulli}(\rho)$ where $\rho$ is the probability above.


If the model estimated β1=−0.32,the formula is:

$$
\widehat{p} = \frac{1}{1 + e^{-(-0.32)}} \approx 0.42
$$


This is the fitted prediction: about 37% of people support Biden, based on the intercept.
​
 

```{r}
#| cache: true
#| message: false
#| warning: false
model <- lm(mpg ~ wt + hp, data = mtcars)
tidy(model, conf.int = TRUE)
```
### Summary:
Public opinion polls provide crucial but imperfect snapshots of voter sentiment during campaigns. Using March 2024 YouGov survey data from 1,559 U.S. adults, we estimate the proportion of votes Joe Biden will receive in the November election.
However, our model relies on the assumption that voter preferences and relationships between variables remain stable from March until election day, which may not hold true.
We model the probability of Biden support (coded as “Yes” or “No”) using a logistic regression model with only an intercept, which estimates the overall average support in the population.


```{r}
# Commented this whole 
# data was not availble
# Will perform operations in 3 chunks
# will find data resource



# #| cache: true
# fit_biden <- logistic_reg(engine = "glm") |>
#   fit(biden ~ 1, data = poll_data)


# tidy(fit_biden, conf.int = TRUE)

# # A Plot
# library(gt)

# fit_biden |> 
#   tidy(conf.int = TRUE) |> 
#   select(term, estimate, conf.low, conf.high) |> 
#   gt() |> 
#   tab_header(title = "Model Results: Biden Support") |> 
#   tab_source_note(source_note = "Data source: March 2024 YouGov Poll")


```

```{r}
#| cache: true
#| message: false
#| warning: false
library(gt)
library(broom)
library(tidyverse)

# Placeholder model using mtcars (as if it were poll_data)
model <- lm(mpg ~ wt + hp, data = mtcars)

# Display the results with poll-style labels
tidy(model, conf.int = TRUE) |> 
  select(term, estimate, conf.low, conf.high) |> 
  gt() |> 
  tab_header(title = "Model Results: Biden Support") |> 
  tab_source_note(source_note = "Data source: March 2024 YouGov Poll (placeholder using mtcars)")

```